---
output: html_document
editor_options: 
  chunk_output_type: console
---
```{r}
library(tidyverse)
library(feather)
library(glue)
library(ggthemes)
library(png)
library(here)
library(mapview)
library(sf)
library(viridis)
library(kableExtra)
library(RColorBrewer)
library(gridExtra)
library(cowplot)

```

#Read in all computed data
```{r}
read_add_site <- function(flux_f){
    
    site_code <- str_split_fixed(flux_f, '/', n = Inf)[,9]

    site_code <- str_split_fixed(site_code, '[.]', n = Inf)[,1]
    fluxes <- read_feather(flux_f) 
    fluxes <- fluxes %>%
        mutate(wy = as.factor(wy),
               flux = as.numeric(flux),
               method = as.character(method),
               site_code = as.character(site_code),
               thin = as.character(thin))
    
    return(fluxes)
}

flux_files <- list.files(here('streamlined/out/'), full.names = TRUE, recursive = T)

fluxes <- map_dfr(flux_files, read_add_site) %>%
    na.omit() #only take complete years
#view(fluxes)
```


#calculate percent difference from 'truth' 
```{r}
truth <- filter(fluxes, method == 'true') %>%
    rename(real = flux) %>%
    select(wy, site_code, real)

coarse <- filter(fluxes, method != 'true')

comp <- left_join(coarse, truth, by = c('wy','site_code')) %>%
    mutate(dif = (real-flux)) %>%
    mutate(percent_dif = (dif/((real+flux)/2))*100) %>%
    na.omit() # if sites are incomplete when read in this gets rid of them

```

#Get metadata and join it in
```{r}
comp_meta <- read_csv("streamlined/data/site/usgs_nitrate_sites.csv") %>%
    right_join(., comp, by = "site_code")%>%
    select(-`...1`, -dataset) %>%
    filter(ws_area_ha < 100000) #filter out big ws

n_site_years <- comp_meta %>%
    select(site_code, wy) %>%
    unique() %>%
    nrow()
```

#Map sites! Mapview not working for no reason.
```{r}
us_base <- map_data('state')

map_points <- comp_meta %>%
    filter(method == 'pw',
           thin == 'daily') %>%
    group_by(site_code) %>%
    slice(1) %>%
    select(-thin, -method) %>%
    mutate(alpha = RBI^2)

n_sites <- nrow(map_points)

site_map <- ggplot()+
    geom_polygon(data = us_base, aes(x=long, y=lat, group = group),
                 color = 'black', fill = 'white')+
    geom_point(data = map_points, aes(x = long, y = lat, fill = RBI),
               size = 4, color = 'black', pch = 21)+
    labs(caption = paste0(n_sites, ' total sites'))+
    theme_few()+
    theme(axis.text.y=element_blank(),
        axis.ticks.y=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        plot.background = element_rect(fill = "black"),
        panel.background = element_rect(fill = "black",
                                colour = "black",
                                size = 0.5, linetype = "solid"))+
    #scale_fill_binned(type = 'viridis', breaks = c(0, .1, .5, .8, 1))
    scale_fill_steps2(low = "yellow", mid = "orange", high = "red", midpoint = .02)
    #scale_fill_viridis(option = 'magma',
                        #direction = -1) 

ggsave(site_map, filename = 'streamlined/plots/site_map.png', width = 6, height = 3)


pal <-  colorRampPalette(brewer.pal(5, "Reds"))
#pal <- colorRampPalette(c("yellow", 'orange', "red"),
#                                space = "rgb")
#mapviewOptions(basemaps = 'Thunderforest.TrasnportDark')
mapviewOptions(basemaps = 'ESRI.WorldImagery')

map <- comp_meta %>%
    filter(method == 'pw',
           thin == 'daily') %>%
    select(-thin, -method) %>%
    mutate(alpha = RBI^2) %>%
    st_as_sf(coords = c('long', 'lat'),
             crs = 4326) %>%
    #st_jitter(factor = 0.05) %>%
    mapview(zcol = 'RBI',
            col.regions = pal, 
            at = c(0, 0.25, .5, .75, 1),
            layer.name = 'RBI',
            alpha = 'alpha',
            map.types = mapviewGetOption("basemaps"))
map

mapview::mapshot(
  map,
  url = NULL,
  file = 'streamlined/plots/map.png',
  remove_controls = c("zoomControl", "layersControl", "homeButton", "scaleBar",
    "drawToolbar", "easyButton"))

   
```

#What ecoregions are represented?
```{r}
length(unique(comp_meta$NA_L2NAME))
ecoregion_table <- comp_meta %>%
    select(wy, site_code, NA_L2NAME,
           RBI, ws_area_ha) %>%
    unique() %>%
    group_by(NA_L2NAME) %>%
    tally() %>%
    arrange(-n) %>%
    rename(Ecoregion = NA_L2NAME,
           `Site Years` = n) %>%
    kbl() %>%
    kable_paper(full_width = F)
```

# Site year by site
```{r}
site_year_hist <- comp_meta %>%
    filter(method == 'pw',
           thin == 'daily') %>%
    select(wy, site_code) %>%
    group_by(site_code) %>%
    tally() %>%
    ggplot(., aes(x = n))+
        geom_histogram(binwidth = 1, color = 'black')+
    scale_x_continuous(breaks = c (2, 4, 6, 8))+
    scale_y_continuous(breaks = c (2, 4, 6, 8, 10))+
    theme_few()+
    labs(x = 'Site Years by Site',
         y = 'Count',
         title = 'Distribution of Site Years')
site_year_hist
ggsave(site_year_hist, filename = 'streamlined/plots/site_year_hist.png')
```

#Make a nice boxplot by thinning interval and method
```{r}
#
comp_meta$thin <- factor(comp_meta$thin, levels=c('daily', 'weekly', 'biweekly', 'monthly', 'quarterly'))
comp_meta$method <- factor(comp_meta$method, levels = c('pw', 'beale', 'rating', 'composite'))

#
method_labs <- c('Period-Weighted', 'Beale Ratio', 'Regression', 'Composite')
names(method_labs) <-  c('pw', 'beale', 'rating', 'composite')

#
n_all <- ggplot(comp_meta, aes(x = thin, y = percent_dif)) + 
    geom_rect(color = '#FFD685',
              fill = '#FFD685',
              alpha = .1,
              aes(ymax = 20, ymin = 10, 
                  xmin = -Inf, xmax = Inf))+
    geom_rect(color = '#7AAC5D',
              fill = '#7AAC5D',
              alpha = .1,
              aes(ymax = 10, ymin = -10, 
                  xmin = -Inf, xmax = Inf))+
    geom_rect(color = '#FFD685',
              fill = '#FFD685',
              alpha = .1,
              aes(ymax = -10, ymin = -20, 
                  xmin = -Inf, xmax = Inf))+
    facet_wrap(~method, 
               ncol  = 2,
               labeller = labeller(method = method_labs)) +
     geom_boxplot(alpha=.5) +
    theme_few() +
    theme(axis.text = element_text(size = 15),
          axis.title = element_text(size = 20),
          strip.text.x = element_text(size = 20),
          plot.caption = element_text(size = 15))+
    labs(x = 'Thinning Interval', 
         y = '% Difffernce from True Nitrate Flux',
         caption = paste0(n_site_years, ' total site years'))
n_all
ggsave(plot = n_all, filename = 'streamlined/plots/overview_boxplot.png', height = 6, width = 10)
```

#Make a nice plot of how watershed area tracks with percent difference across quarterly data
```{r}
ggplot(filter(comp_meta, thin == 'quarterly'), 
       aes(x = ws_area_ha/100, y = percent_dif))+
    geom_point()+
    scale_x_log10()+
    facet_wrap(~method,
               labeller = labeller(method = method_labs))+
    theme_few()+
    labs(x = 'Watershed Area (square km, log)', 
         y = '% Difffernce from True Nitrate Flux',
         caption = paste0(n_site_years, ' total site years'))
```

#Make a nice plot of how RBI tracks with percent difference across biweekly data
```{r}
#cor(comp_meta$ws_area_ha, comp_meta$RBI)
#cor(comp_meta$RBI, comp_meta$percent_dif)
ggplot(filter(comp_meta, thin == 'quarterly'), 
       aes(x = RBI, y = abs(percent_dif)))+
    geom_point()+
    scale_x_log10()+
    facet_wrap(~method,
               labeller = labeller(method = method_labs))+
    theme_few()+
    labs(x = 'Flashiness (RBI)', 
         y = '% Difffernce from True Flux (absolute)',
         caption = paste0(n_site_years, ' total site years'))
```

# Make bespoke coarsening illustration. Note that this plot will only work with by loading 'coarse_illustration.RData' first. Coarse data is the 
```{r}
coarse_data <- rbind(
    mutate(thinned_daily_c, thin = 'daily'),
    mutate(thinned_weekly_c, thin = 'weekly'),
    mutate(thinned_biweekly_c, thin = 'biweekly'),
    mutate(thinned_monthly_c, thin = 'monthly'),
    mutate(thinned_quarterly_c, thin = 'quarterly'))
prep_data_q

coarse_data$thin <- factor(coarse_data$thin, levels=c('daily', 'weekly', 'biweekly', 'monthly', 'quarterly'))

#
title_size <- 15
lab_size <- 10
    
p1 <- ggplot(prep_data_q, aes(x =date, y = q_lps),)+
    geom_line(color = 'blue')+
    scale_y_log10()+
    theme_few()+
    theme(axis.title.x = element_blank(),
          plot.title = element_text(size = title_size,hjust = 0.5),
          axis.text.y = element_text(size = lab_size),
          axis.text.x = element_blank())+
    labs(title = 'Flow',
         y = 'Lps')
p1

p2 <- ggplot(thinned_daily_c, aes(x = date, y = con))+
    geom_line(color = 'darkgreen')+
    geom_point(color = 'darkgreen')+
    theme_few()+
    scale_y_continuous(limits = c(0,20))+
    theme(axis.title.x = element_blank(),
          plot.title = element_text(size = title_size,hjust = 0.5),
          axis.text.y = element_text(size = lab_size),
          axis.text.x = element_blank()) +
    labs(title = 'Daily',
         y = '')
p2

p3 <- ggplot(thinned_weekly_c, aes(x = date, y = con))+
    geom_line(color = 'darkgreen')+
    geom_point(color = 'darkgreen')+
    theme_few()+
    scale_y_continuous(limits = c(0,20))+
    theme(axis.title.x = element_blank(),
          axis.text.y = element_text(size = lab_size),
          plot.title = element_text(size = title_size,hjust = 0.5),
          axis.text.x = element_blank()) +
    labs(title = 'Weekly',
         y = '')
p3

p4 <- ggplot(thinned_biweekly_c, aes(x = date, y = con))+
    geom_line(color = 'darkgreen')+
    geom_point(color = 'darkgreen')+
    theme_few()+
    scale_y_continuous(limits = c(0,20))+
    theme(axis.title.x = element_blank(),
          axis.text.y = element_text(size = lab_size),
          plot.title = element_text(size = title_size,hjust = 0.5),
          axis.text.x = element_blank()) +
    labs(title = 'Biweekly',
         y = 'mg/L')
p4

p5 <- ggplot(thinned_monthly_c, aes(x = date, y = con))+
    geom_line(color = 'darkgreen')+
    geom_point(color = 'darkgreen')+
    theme_few()+
    scale_y_continuous(limits = c(0,20))+
    theme(axis.title.x = element_blank(),
          axis.text.y = element_text(size = lab_size),
          plot.title = element_text(size = title_size,hjust = 0.5),
          axis.text.x = element_blank()) +
    labs(title = 'Monthly',
         y = '')
p5

p6 <- ggplot(thinned_quarterly_c, aes(x = date, y = con))+
    geom_line(color = 'darkgreen')+
    geom_point(color = 'darkgreen')+
    theme_few()+
    scale_y_continuous(limits = c(0,20))+
    theme(plot.title = element_text(size = title_size,hjust = 0.5),
          axis.text.y = element_text(size = lab_size)) +
    labs(title = 'Quarterly',
         y = '',
         x = 'Date')
p6

allplotslist <- align_plots(p1,p2, p3, p4, p5, p6, align = 'hv')

p_all <- grid.arrange(allplotslist[[1]], allplotslist[[2]], allplotslist[[3]],
             allplotslist[[4]], allplotslist[[5]], allplotslist[[6]], 
             ncol = 1, padding = unit(00))

ggsave(p_all, filename = 'streamlined/plots/coarse_illustration.png', width = 10, height = 8)

####J ###

p1 <- ggplot(prep_data_q, aes(x =date, y = q_lps),)+
    geom_line(color = 'blue')+
    scale_y_log10()+
    theme_few()
p1
##devtools::install_github('bbc/bbplot')
p2 <- ggplot(coarse_data, aes(x = date, y = con))+
    geom_line(color = 'darkgreen')+
    geom_point(color = 'darkgreen')+
    facet_wrap(~thin, ncol = 1)+
    bbc_style() 
p2

p3 <- ggplot()+
    geom_line(data=prep_data_q, aes(x =date, y = q_lps), color = 'blue')+
  ## scale_y_log10()
    theme_few()

p4 <- p3 + geom_line(data=coarse_data, aes(x = date, y = con/.02),color = 'darkgreen')+
    geom_point(data=coarse_data, aes(x = date, y = con/.02),color = 'darkgreen')+
    facet_wrap(~thin, ncol = 1) +
      scale_y_continuous(
                         sec.axis = sec_axis(~ . *.02))
    theme_few()
p4
```

